Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-10 popl24/hyperprop.tex
checkpoint

The simulator is represented by a probabilistic algorithm $\SIM_C$,
aka a \emph{simulation}, that is parameterized by corrupt inputs and
the output of an ideal functionality, and that returns a set of
adversarial views (as a memory) with some probability. Given
corrupt inputs $\store$ and ideal functionality output $v$,  
we write:
$$
\prob(\SIM_C(\store,v) = \store')
$$
to denote the probability that $\SIM_C(\store,v)$
returns corrupt views $\store'$ as a result. We can then define the
probability distribution of corrupt views reconstructed
by the simulator as follows:
\begin{definition}
  Given $C$, $\store$, and $v$, we write $\progd(\SIM_C(\store,v))$ to
  denote the distribution of corrupt views reconstructed by the
  simulation, where for
  all $\store' \in \mems(V)$:
  $$
  \progd(\SIM_C(\store,v))(\store')\ \defeq\ \prob(\SIM_C(\store,v) = \store') 
  $$
\end{definition}

@@

Probabilistic noninterference can also be restated to formally capture a
basic intuition that noninterfering programs do not provide
the adversary with any clues about honest secrets through corrupt
views, as in the following Lemma. This is similar to asserting that
adversarial knowledge is not increased by the execution of a program as in formulations
of so-called gradual release \cite{4223226}. 
\begin{lemma}
  \label{lemma-pni}
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, 
  $\prog$ satisfies probabilistic noninterference iff for all
  $\store \in \mems(S \cup V)$:
  $$\condd{\progd(\prog)}{S_H}{\store_{S_C}} =
    \condd{\progd(\prog)}{S_H}{\store_{(S\cup V)_C}} $$
\end{lemma}

@@

From an information flow perspective, we can say that a $\NIMO$
protocol does not release information beyond what is declassified
via the public output. From a real/ideal perspective, we can
observe that $\NIMO$ implies that the simulator can use
the protocol itself to reconstruct the distribution of adversarial
views. That is, given the output of the ideal functionality
$\idealf(\store_S)$, the simulator can randomly choose any
$\store'$ such that $\store' =_C \store$ and $\idealf(\store'_S) =
\idealf(\store_S)$ and run the protocol with initial memory $\store'$-
$\NIMO$ guarantees ideal reconstruction of the real-world corrupt views. 
 However, there is a subtlety here in that the adversary
must be able to tractably reconstruct this knowledge. This is not
generally true, in particular, if $\idealf$ is a 1-way
function. Define:
\begin{definition}[Ideal Knowledge]
  Given a functionality $\idealf$ and output value $v$, the associated
  \emph{ideal knowledge}, denoted $\ik(\idealf,v)$ is:
  $$
  \{ \store\ |\ \idealf(\store) = v \}
  $$
  We say that $\idealf$ is \emph{pre-imageable} iff $\ik(\idealf, v)$ for all
  $v$ can be computed tractably.
\end{definition}
Now we can show our main result, that noninterference modulo output,
together with the assumption that $\idealf$ is pre-imageable, implies
passive security of a protocol.
\begin{theorem}
  \label{theorem-nimo}
  Assume given pre-imageable $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\NIMO(\prog)$
  then $\prog$ is passive secure.
\end{theorem}

\begin{proof}
  Let $H$ and $C$ be an arbitrary partition of the federation and
  suppose $\prog$ satisfies noninterference modulo output. Let
  $\iov(\prog) = (V,S)$ and $\flips(\prog) = F$ with output view $x
  \in V$ and let $\store$ be an arbitrary element of $\mems(S \cup
  F)$. Then the distribution of adversarial views in the real world
  is, by definition:
  $$\condd{\progd(\prog)}{V_C}{\store_S}$$

@@

  Now, since the random tape is selected in simulation from the same distribution
  that we assume for the real world, after selection of $\store'$ the
  probability that any particular $\store^{\SIM}_{V_C}$ is returned is by definition:
  $$
  \progd(\prog)(\store^{\SIM}_{V_C} | \store')
  $$
  Furthermore, since we assume that $\prog$ correctly implements $\idealf$, this
  means:
  $$
  \store_S =_C \store' \wedge
     \condd{\progd(\prog)}{\{ \outv \}}{\store_S} =
     \condd{\progd(\prog)}{\{ \outv \}}{\store'}
  $$
  so by the definition of noninterference modulo output,
  any choice of $\store'$ yields the same distribution $\condd{\progd(\prog)}{V_C}{\store_S}$.
  Therefore by definition
  $
   \progd(\SIM_C(\store_{S_C},\idealf(\store))) = \condd{\progd(\prog)}{V_C}{\store_S}
  $.
\end{proof}

>>>>

The simulator is represented by a probabilistic algorithm $\SIM_C$,
aka a \emph{simulation}, that is parameterized by corrupt inputs and
the output of an ideal functionality, and that returns a set of
adversarial views (as a memory) with some probability. Given
corrupt inputs $\store$ and ideal functionality output $v$,  
we write
$
\prob(\SIM_C(\store,v) = \store')
$
to denote the probability that $\SIM_C(\store,v)$
returns corrupt views $\store'$ as a result. We can then define the
probability distribution of corrupt views reconstructed
by the simulator as follows:
\begin{definition}
  Given $C$, $\store$, and $v$, we write $\progd(\SIM_C(\store,v))$ to
  denote the distribution of corrupt views reconstructed by the
  simulation, where for
  all $\store' \in \mems(V)$:
  $$
  \progd(\SIM_C(\store,v))(\store')\ \defeq\ \prob(\SIM_C(\store,v) = \store') 
  $$
\end{definition}

@@

Probabilistic noninterference can also be restated to formally capture a
basic intuition that noninterfering programs do not provide
the adversary with any clues about honest secrets through corrupt
views, as in the following Lemma. This is similar to asserting that
adversarial knowledge is not increased by the execution of a program as in formulations
of so-called gradual release \cite{4223226}. 
\begin{lemma}
  \label{lemma-pni}
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, 
  $\prog$ satisfies probabilistic noninterference iff for all
  $\store \in \mems(S \cup V)$,
  $\condd{\progd(\prog)}{S_H}{\store_{S_C}} =
    \condd{\progd(\prog)}{S_H}{\store_{(S\cup V)_C}}$.
\end{lemma}

@@

From an information flow perspective, we can say that a $\NIMO$
protocol does not release information beyond what is declassified
via the public output. From a real/ideal perspective, we can
observe that $\NIMO$ implies that the simulator can use
the protocol itself to reconstruct the distribution of adversarial
views. That is, given the output of the ideal functionality
$\idealf(\store_S)$, the simulator can randomly choose any
$\store'$ such that $\store' =_C \store$ and $\idealf(\store'_S) =
\idealf(\store_S)$ and run the protocol with initial memory $\store'$-
$\NIMO$ guarantees ideal reconstruction of the real-world corrupt views. 
 However, there is a subtlety here in that the adversary
must be able to tractably reconstruct this knowledge. This is not
generally true, in particular, if $\idealf$ is a 1-way
function. Define:
\begin{definition}[Ideal Knowledge]
  Given a functionality $\idealf$ and output value $v$, the associated
  \emph{ideal knowledge}, denoted $\ik(\idealf,v)$ is
  $
  \{ \store\ |\ \idealf(\store) = v \}
  $.
  We say that $\idealf$ is \emph{pre-imageable} iff $\ik(\idealf, v)$ for all
  $v$ can be computed tractably.
\end{definition}
Now we can show our main result, that noninterference modulo output,
together with the assumption that $\idealf$ is pre-imageable, implies
passive security of a protocol.
\begin{theorem}
  \label{theorem-nimo}
  Assume given pre-imageable $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\NIMO(\prog)$
  then $\prog$ is passive secure.
\end{theorem}

\begin{proof}
  Let $H$ and $C$ be an arbitrary partition of the federation and
  suppose $\prog$ satisfies noninterference modulo output. Let
  $\iov(\prog) = (V,S)$ and $\flips(\prog) = F$ with output view $x
  \in V$ and let $\store$ be an arbitrary element of $\mems(S \cup
  F)$. Then the distribution of adversarial views in the real world
  is, by definition,
  $\condd{\progd(\prog)}{V_C}{\store_S}$.

@@

  Now, since the random tape is selected in simulation from the same distribution
  that we assume for the real world, after selection of $\store'$ the
  probability that any particular $\store^{\SIM}_{V_C}$ is returned is by definition
  $
  \progd(\prog)(\store^{\SIM}_{V_C} | \store')
  $.
  Furthermore, since we assume that $\prog$ correctly implements $\idealf$, this
  means
  $
  \store_S =_C \store' \wedge
     \condd{\progd(\prog)}{\{ \outv \}}{\store_S} =
     \condd{\progd(\prog)}{\{ \outv \}}{\store'}
  $,
  so by the definition of noninterference modulo output,
  any choice of $\store'$ yields the same distribution $\condd{\progd(\prog)}{V_C}{\store_S}$.
  Therefore by definition
  $
   \progd(\SIM_C(\store_{S_C},\idealf(\store))) = \condd{\progd(\prog)}{V_C}{\store_S}
  $.
\end{proof}

### 2023-07-10 popl24/metalang.tex
checkpoint

The $\TirName{FnT}$ and $\TirName{Appt}$ rules apply to function
definition and application respectively, and rely on the
definition of function input type annotations $\tas$ and
type term substitutions $\sigma$. 
\begin{definition}
  A \emph{function input type annotation} $\tas$ is a mapping from
  function names $f$ to type products $\tau_1 * \cdots * \tau_n$.
  A \emph{type term substitution} $\sigma$ is a mapping from
  $\minifed$ variables $x$ to values, where $\sigma(\tau)$ denotes
  the replacement of occurences of $x$ in $\tau$ with $\sigma(x)$. 
\end{definition}
We assume that input type annotations $\tas$ are provided by the
programmer for all function definitions. This guarantees that
$\metaprot$ type checking is straightforward and efficient.
Function types are of the form:
$$
\tau_1 * \cdots * \tau_n \rightarrow \tau,\viewst
$$
where $\viewst$ denotes the effect of the function on the residual
program.  The function type can be understood as a dependent $\Pi$
type, with every term variable bound. When applied, these variables
are instantiated with a type term substitution $\sigma$. In our
implementation, we adapt \emph{synthesis} as defined in Dependent ML \cite{10.1145/292540.292560}
to obtain this $\sigma$- essentially this is a match on the syntactic
structure of types and expressions. 
\begin{example}
  Given $\ttt{share3}$ as defined in Example \ref{example-share3} and
  annotation:
  $$\tas(\ttt{share3}) =  \ttt{cid(client)}\ *\ \ttt{string(sid)}$$
  the type of $\ttt{share3}$ is $\tas(\ttt{share3}) \rightarrow \tau,\varnothing$
  where $\tau$ is:
  $$
  \ttt{\{ s1 : bool[client]; s2 : bool[client]; s3 : bool[client] \}}
  $$
\end{example}

>>>>

The $\TirName{FnT}$ and $\TirName{Appt}$ rules apply to function
definition and application respectively, and rely on the
definition of function input type annotations $\tas$ and
type term substitutions $\sigma$. 
\begin{definition}
  A \emph{function input type annotation} $\tas$ is a mapping from
  function names $f$ to type products $\tau_1 * \cdots * \tau_n$.
  A \emph{type term substitution} $\sigma$ is a mapping from
  $\minifed$ variables $x$ to values, where $\sigma(\tau)$ denotes
  the replacement of occurences of $x$ in $\tau$ with $\sigma(x)$. 
\end{definition}
We assume that input type annotations $\tas$ are provided by the
programmer for all function definitions. This guarantees that
$\metaprot$ type checking is straightforward and efficient.
Function types are of the form
$
(\tau_1 * \cdots * \tau_n \rightarrow \tau,\viewst)
$,
where $\viewst$ denotes the effect of the function on the residual
program.  The function type can be understood as a dependent $\Pi$
type, with every term variable bound. When applied, these variables
are instantiated with a type term substitution $\sigma$. In our
implementation, we adapt \emph{synthesis} as defined in Dependent ML \cite{10.1145/292540.292560}
to obtain this $\sigma$- essentially this is a match on the syntactic
structure of types and expressions. 
\begin{example}
  Given $\ttt{share3}$ as defined in Example \ref{example-share3} and
  annotation:
  $$\tas(\ttt{share3}) =  \ttt{cid(client)}\ *\ \ttt{string(sid)}$$
  the type of $\ttt{share3}$ is $\tas(\ttt{share3}) \rightarrow \tau,\varnothing$
  where $\tau$ is:
  $$
  \ttt{\{ s1 : bool[client]; s2 : bool[client]; s3 : bool[client] \}}
  $$
\end{example}

### 2023-07-10 popl24/minicat.tex
checkpoint

Expression forms include the convenience
$\select{\be_1}{\be_2}{\be_3}$, which is essentially a conditional
expression with:
$$
\select{\be_1}{\be_2}{\be_3} \equiv (\be_1\ \eand\ \be_2)\ \eor\ (\enot\ \be_1\ \eand\ \be_3)
$$
We also include \emph{oblivious transfer} $\OT{\be_1}{\be_2}{\be_3}$ as a primitive,
with semantics similar to $\ttt{select}$ but with important nuances
related to communication between clients as we discuss more below.
As we will demonstrate, it is not necessary to include $\ttt{OT}$
as a primitive since we can implement it in a provably secure
fashion. However, its inclusion simplifies our presentation and is a useful
convenience.

@@

\begin{fpfig}[t]{$\minifed$ expression interpretation.}{fig-minifed-interp}
  {\small
  $$
  \begin{array}{cc}
    \begin{array}{rcl}
      \lcod{\store, \etrue}{\cid} &=& 1\\
      \lcod{\store, \efalse}{\cid} &=& 0\\
      \lcod{\store, \flip{\cid}{w}}{\cid} &=& \store(\flip{\cid}{w})\\
      \lcod{\store, \secret{\cid}{w}}{\cid} &=& \store(\secret{\cid}{w})
    \end{array} & 
    \begin{array}{rcl}
      \lcod{\store, \view{\cid}{w}}{\cid} &=& \store(\view{\cid}{w})\\
      \lcod{\store, \oracle{w}}{\cid} &=& \store(\oracle{w})\\
      \lcod{\store, \enot\ \be}{\cid} &=& \cod{\enot\ \lcod{\store,\be}{\cid}}\\
      \lcod{\store, \be_1\ \mathit{binop}\ \be_2}{\cid} &=&
      \cod{\lcod{\store,\be_1}{\cid}\ \mathit{binop}\ \lcod{\store,\be_2}{\cid}}
    \end{array}
  \end{array}
  $$
  $$
  \lcod{\store, \select{\be_1}{\be_2}{\be_3}}{\cid} =
  \begin{cases}
    \lcod{\store,\be_2}{\cid} & \text{if\ } \lcod{\store,\be_1}{\cid}\\
    \lcod{\store,\be_3}{\cid} & \text{if\ } \neg\lcod{\store,\be_1}{\cid}
  \end{cases}%\\
      %\lcod{\store, \OT{\be_1}{\be_2}{\be_3}}{\cid} &=&
      %             \begin{cases}
      %                \lcod{\store,\be_2}{\cid'} & \text{if\ } \lcod{\store,\be_1}{\cid}\\
      %                \lcod{\store,\be_3}{\cid'} & \text{if\ } \neg\lcod{\store,\be_1}{\cid}
      %             \end{cases}
  $$
  }
\end{fpfig}

Evaluation of configurations is then defined via a small-step reduction relation $\redx$.
This is defined in the obvious manner for view assignments other than through
$\ttt{OT}$- however note that reduction requires that views are never reassigned. 
\begin{mathpar}
  (\store, \eassign{\view{\cid}{w}}{\be};\prog) \redx (\extend{\store}{\view{\cid}{w}}{\lcod{\store,\be}{\cid'}}, \prog)
\end{mathpar}
For view assignments through $\ttt{OT}$, we define a different reduction rule that
captures the appropriate semantics- that is, the selection bit is \emph{not} communicated
to the sender (through a view assignment), and only the selected bit is sent to the receiver:
\begin{mathpar}
  \inferrule
  {\beta = \text{if\ } \lcod{\store,\be_1}{\cid}  \text{\ then\ } \lcod{\store,\be_2}{\cid'} \text{\ else\ } \lcod{\store,\be_3}{\cid'}}
      {(\store, \eassign{\view{\cid}{w}}{\OT{\be_1}{\be_2}{\be_3}};\prog) \redx (\extend{\store}{\view{\cid}{w}}{\beta}, \prog)}
\end{mathpar}
We define $\redxs$ as the reflexive, transitive closure of $\redx$.

>>>>

Expression forms include the convenience
$\select{\be_1}{\be_2}{\be_3}$, which is essentially a conditional
expression with
$
\select{\be_1}{\be_2}{\be_3} \equiv (\be_1\ \eand\ \be_2)\ \eor\ (\enot\ \be_1\ \eand\ \be_3)
$.
We also include \emph{oblivious transfer} $\OT{\be_1}{\be_2}{\be_3}$ as a primitive,
with semantics similar to $\ttt{select}$ but with important nuances
related to communication between clients as we discuss more below.
As we will demonstrate, it is not necessary to include $\ttt{OT}$
as a primitive since we can implement it in a provably secure
fashion. However, its inclusion simplifies our presentation and is a useful
convenience.

@@

\begin{fpfig}[t]{$\minifed$ expression interpretation (T) and reduction (B) rules.}{fig-minifed-interp}
  {\small
  $$
  \begin{array}{cc}
    \begin{array}{rcl}
      \lcod{\store, \etrue}{\cid} &=& 1\\
      \lcod{\store, \efalse}{\cid} &=& 0\\
      \lcod{\store, \flip{\cid}{w}}{\cid} &=& \store(\flip{\cid}{w})\\
      \lcod{\store, \secret{\cid}{w}}{\cid} &=& \store(\secret{\cid}{w})
    \end{array} & 
    \begin{array}{rcl}
      \lcod{\store, \view{\cid}{w}}{\cid} &=& \store(\view{\cid}{w})\\
      \lcod{\store, \oracle{w}}{\cid} &=& \store(\oracle{w})\\
      \lcod{\store, \enot\ \be}{\cid} &=& \cod{\enot\ \lcod{\store,\be}{\cid}}\\
      \lcod{\store, \be_1\ \mathit{binop}\ \be_2}{\cid} &=&
      \cod{\lcod{\store,\be_1}{\cid}\ \mathit{binop}\ \lcod{\store,\be_2}{\cid}}
    \end{array}
  \end{array}
  $$
  $$
  \lcod{\store, \select{\be_1}{\be_2}{\be_3}}{\cid} =
  \begin{cases}
    \lcod{\store,\be_2}{\cid} & \text{if\ } \lcod{\store,\be_1}{\cid}\\
    \lcod{\store,\be_3}{\cid} & \text{if\ } \neg\lcod{\store,\be_1}{\cid}
  \end{cases}%\\
      %\lcod{\store, \OT{\be_1}{\be_2}{\be_3}}{\cid} &=&
      %             \begin{cases}
      %                \lcod{\store,\be_2}{\cid'} & \text{if\ } \lcod{\store,\be_1}{\cid}\\
      %                \lcod{\store,\be_3}{\cid'} & \text{if\ } \neg\lcod{\store,\be_1}{\cid}
      %             \end{cases}
  $$
  \vspace{1mm}

  \rule{130mm}{0.5pt}

  \begin{mathpar}
    (\store, \eassign{\view{\cid}{w}}{\be};\prog) \redx (\extend{\store}{\view{\cid}{w}}{\lcod{\store,\be}{\cid'}}, \prog)

      \inferrule
  {\beta = \text{if\ } \lcod{\store,\be_1}{\cid}  \text{\ then\ } \lcod{\store,\be_2}{\cid'} \text{\ else\ } \lcod{\store,\be_3}{\cid'}}
      {(\store, \eassign{\view{\cid}{w}}{\OT{\be_1}{\be_2}{\be_3}};\prog) \redx (\extend{\store}{\view{\cid}{w}}{\beta}, \prog)}    
\end{mathpar}
  }
\end{fpfig}

Evaluation of configurations is then defined via a small-step reduction relation $\redx$,
also shown in Figure \ref{fig-minifed-interp}.
This is defined in the obvious manner for view assignments other than through
$\ttt{OT}$- however note that reduction requires that views are never reassigned. 
For view assignments through $\ttt{OT}$, we define a different reduction rule that
captures the appropriate semantics- that is, the selection bit is \emph{not} communicated
to the sender (through a view assignment), and only the selected bit is sent to the receiver:
We define $\redxs$ as the reflexive, transitive closure of $\redx$.

### 2023-07-10 popl24/pmf.tex
checkpoint

\begin{definition}
  Given $\margd{\pmf}{X}$, its \emph{conditional distribution given
  $\stores$} with $\dom(\stores) = Y$ with $Y \subseteq X$, denoted
  $\condd{\pmf}{X}{\stores}$, is a distribution with domain $X$ where for all
  $\store \in \mems(X)$:
  $$
  \condd{\pmf}{X}{\stores}(\store) =
  (\sum_{\store' \in \stores} \margd{\pmf}{X}(\store \cap \store')) /
  (\sum_{\store' \in \stores} \margd{\pmf}{Y}(\store'))
  $$
  where $\margd{\pmf}{X}(\store \cap \store')) = 0$ if $\store \cap \store'$ is undefined.
\end{definition}
To recover familiar notation we allow the following syntactic
sugarings:
\begin{eqnarray*}
  \condd{\pmf}{X}{\store}  &\defeq& \condd{\pmf}{X}{\{ \store\}}\\
  \pmf(\store)  &\defeq& \margd{\pmf}{X}(\store)  \qquad \dom(\store) = X\\
  \pmf(\store|\stores)  &\defeq& \condd{\pmf}{X}{\stores}(\store) \qquad \dom(\store) = X
\end{eqnarray*}

@@

We consider random tapes to be selected from a uniform distribution.
In our threat model, we will also assume that any possible initial
secrets are equally likely when formulating the program distribution.
In this setting, given a program $\prog$ with $\iov(\prog) = S \cup
V$ and $\flips(\prog) = F$ we will consider all $\store
\in \mems(S \cup V \cup F)$ such that
$
\config{\store_{S \cup F}}{\prog} \redxs \config{\store_}{\varnothing}
$
to be equally probable, establishing the basic distribution of the
program. From this, we can immediately derive the marginal distribution
of $S \cup V$ to reason about dependencies between secrets and views. 
\begin{definition}
  \label{def-progd}
  \label{definition-progd}
  Given program $\prog$ with $\iov(\prog) = (S,V)$ and $\flips(\prog) = F$, define $\stores$ as:
  $$
  \stores \defeq \{ \store \mid (\dom(\store) = S \cup V \cup F) \wedge (\store_{S \cup F},\prog) \redxs (\store,\varnothing) \}
  $$
  We note immediately that $|\stores| = 2^{S \cup F}$ given the (deterministic) definition of $\redx$. 
  Define also $\pmf$ as the program's \emph{basic distribution} such that for all
  $\store \in \mems(S \cup V \cup F)$:
  $$
  \pmf(\store) =
  \begin{cases}
    1 / |\stores| & \text{if}\ \store \in \stores\\
    0 & \text{otherwise}
  \end{cases}
  $$
  Then the \emph{program distribution of $\prog$}, denoted $\progd(\prog)$, is the
  marginal distribution of $S \cup V$ in $\prog$'s basic distribution:
  $$
  \progd(\prog) =  \margd{\pmf}{S\cup V}
  $$
  In some cases, we will also be concerned with the (joint)
  probabilities of expression interpretation given a preceding program
  execution, and we write $\progd(\prog, \be)$ to denote the program
  distribution $\progd(\prog;\eassign{\itv}{\be})$ where $\itv$ is a
  special variable that is never used in programs.
\end{definition}

>>>>

\begin{definition}
  Given $\margd{\pmf}{X}$, its \emph{conditional distribution given
  $\stores$} with $\dom(\stores) = Y$ with $Y \subseteq X$, denoted
  $\condd{\pmf}{X}{\stores}$, is a distribution with domain $X$ where for all
  $\store \in \mems(X)$:
  $$
  \condd{\pmf}{X}{\stores}(\store) =
  (\sum_{\store' \in \stores} \margd{\pmf}{X}(\store \cap \store')) /
  (\sum_{\store' \in \stores} \margd{\pmf}{Y}(\store'))
  $$
  where $\margd{\pmf}{X}(\store \cap \store')) = 0$ if $\store \cap \store'$ is undefined.
\end{definition}
To recover familiar notation we allow the syntactic
sugarings $\condd{\pmf}{X}{\store}  \defeq \condd{\pmf}{X}{\{ \store\}}$, and
$\pmf(\store)  \defeq \margd{\pmf}{X}(\store)$ and $\pmf(\store|\stores) \defeq
\condd{\pmf}{X}{\stores}(\store)$ where $\dom(\store) = X$.
%\begin{eqnarray*}
%  \condd{\pmf}{X}{\store}  &\defeq& \condd{\pmf}{X}{\{ \store\}}\\
%  \pmf(\store)  &\defeq& \margd{\pmf}{X}(\store)  \qquad \dom(\store) = X\\
%  \pmf(\store|\stores)  &\defeq& \condd{\pmf}{X}{\stores}(\store) \qquad \dom(\store) = X
%\end{eqnarray*}

@@

We consider random tapes to be selected from a uniform distribution.
In our threat model, we will also assume that any possible initial
secrets are equally likely when formulating the program distribution.
In this setting, given a program $\prog$ with $\iov(\prog) = S \cup
V$ and $\flips(\prog) = F$ we will consider all $\store
\in \mems(S \cup V \cup F)$ such that
$
\config{\store_{S \cup F}}{\prog} \redxs \config{\store_}{\varnothing}
$
to be equally probable, establishing the basic distribution of the
program. From this, we can immediately derive the marginal distribution
of $S \cup V$ to reason about dependencies between secrets and views. 
\begin{definition}
  \label{def-progd}
  \label{definition-progd}
  Given program $\prog$ with $\iov(\prog) = (S,V)$ and $\flips(\prog) = F$, define $\stores$ as:
  $$
  \stores \defeq \{ \store \mid (\dom(\store) = S \cup V \cup F) \wedge (\store_{S \cup F},\prog) \redxs (\store,\varnothing) \}
  $$
  We note immediately that $|\stores| = 2^{S \cup F}$ given the (deterministic) definition of $\redx$. 
  Define also $\pmf$ as the program's \emph{basic distribution} such that for all
  $\store \in \mems(S \cup V \cup F)$:
  $$
  \pmf(\store) =  1 / |\stores| \ \text{if}\ \store \in \stores, \text{otherwise}\ 0
  %\begin{cases}
  %  1 / |\stores| & \text{if}\ \store \in \stores\\
  %  0 & \text{otherwise}
  %\end{cases}
  $$
  Then the \emph{program distribution of $\prog$}, denoted $\progd(\prog)$, is the
  marginal distribution of $S \cup V$ in $\prog$'s basic distribution, i.e., 
  $
  \progd(\prog) \defeq  \margd{\pmf}{S\cup V}
  $.
  In some cases, we will also be concerned with the (joint)
  probabilities of expression interpretation given a preceding program
  execution, and we write $\progd(\prog, \be)$ to denote the program
  distribution $\progd(\prog;\eassign{\itv}{\be})$ where $\itv$ is a
  special variable that is never used in programs.
\end{definition}
